\documentclass{main}

\setname{Daniel}{Moreno Levy}
\setaddress{North Wales, PA}
\setmobile{+1 (707) 871-1906}
\setmail{danielmorenolevy@gmail.com}
\setposition{Software Engineer}
\setcitezenship{USA / Spain Dual Citizen}
\setlinkedinaccount{https://www.linkedin.com/in/daniellevymoreno/}
\setgithubaccount{https://github.com/danilevy1212}
\setthemecolor{Cerulean}

\begin{document}
% Create header
\headerview

% Sections
%
% Summary
\addblocktext{Summary}{
  \begin{addmargin}[0cm]{0.66cm}
      \hspace{4ex} Experienced Software Engineer and Tech Lead proficient in Typescript and Python, with an evolving expertise in Golang and Rust, demonstrated through projects on my \href{https://github.com/danilevy1212}{GitHub}.
  \end{addmargin}
}

% Skills
\addblocktext{Skills}{
  \createskills{
    \createskill{Programming Languages}{
      python \cpshalf typescript \cpshalf rust \cpshalf golang \cpshalf bash \cpshalf lua
    }
    \createskill{Development environments}{
      node / npm \cpshalf poetry / pipenv \cpshalf cargo \cpshalf linux \cpshalf NixOS \cpshalf neoVim
    }
    \createskill{Software Development Insights}{
      Design Patterns \cpshalf CD/CI \cpshalf UNIX Philosophy \cpshalf Infrastructure as Code
    }
    \createskill{Frameworks \ \& \ Libraries}{
      \cpshalf Express \cpshalf NestJS \cpshalf Tokio \cpshalf Gin Django \cpshalf Flask \cpshalf Vue \cpshalf React
    }
    \createskill{Data Bases}{
      PostgreSQL \cpshalf MongoDB \cpshalf redis \cpshalf Elastic Search \cpshalf Graphql
    }
    \createskill{Infrastructure}{
      Docker \cpshalf Kubernetes \cpshalf AWS \cpshalf microservices \cpshalf serverless \cpshalf Gilab CI / CD
    }
    \createskill{Interpersonal}{
      Positivity  \cpshalf Tenacity \cpshalf Clear Communication \cpshalf Teamwork \cpshalf Leadership
    }
    \createskill{Languages} {
      \textbfColor{\emph{Native:}} English \cpshalf Spanish \ \ \textbfColor{\emph{Advanced:}} Japanese, Nôken 2, Dec 2022
    }
  }
}

% Experience
\section{Experience}
\datedexperience{\href{https://www.autopay.com/}{Autopay}}{November 2022 - Present}
\explanation{\textbfColor{Tech Lead}\emphColor{-\ \ \ Backend Engineering Team. }}
\createbullets{
  {
    Promoted due to initiative in modernizing a critical legacy monorepo, leading to improved project health and team efficiency.
  },
  {
    Spearheaded adoption of serverless architecture, breaking down monolithic services into smaller, more manageable units, improving scalability and developer experience.
  },
  {
    Conducted extensive analysis and documentation of critical legacy code, improving our understanding and ability to extend it efficiently.
  },
  {
    Established a comprehensive 'developer wiki' on Confluence, breaking down silos and fostering knowledge sharing across engineering teams.
  },
  {
    Designed and implemented an 'auto-submission' event driven system to automate the loan application process, previously done manually, enhancing operational efficiency.
  },
  {
    Revitalized a large legacy monorepo by replacing ineffective FlowJS with TypeScript, greatly enhancing static code analysis and developer experience. 
  }
}
%
\datedexperience{\href{https://www.autopay.com/}{Autopay}}{July 2022 - November 2022}
\explanation{\textbfColor{Backend Engineer}\emphColor{-\ \ \ Backend Engineering Team. }}
\createbullets{
  {
    Developed several APIs to support the new car loan application process, including SNS / SQS based event driven lambdas and REST servers.
  },
  {
    Took ownership of manual mail code import process, semi-automating it with Gitlab CI / CD to reduce the time required to import new codes by 90\%.
  }
}
%
\datedexperience{\href{https://bambu.co/}{Bambu}}{January 2022 - June 2022}
\explanation{\textbfColor{Backend Engineer}\emphColor{-\ \ \ Backend Engineering Team. }}
\createbullets{
  {
    Managed the deployment and ongoing maintenance of Kubernetes clusters, ensuring reliable delivery of financial services APIs to a global client base.
  },
  {
    Collaborated effectively within a diverse, international team, customizing Bambu's Robo Advisor to meet unique requirements of clients worldwide.
  }
}
%
\datedexperience{\href{https://rebellionpay.com/en}{Rebellion Pay}}{November 2020 - November 2021}
\explanation{\textbfColor{Software Engineer}\emphColor{-\ \ \ Backend Engineering Team. }}
\createbullets{
  {
    Lead the design and development of key systems for Rebellion Pay's financial services, such as cryptocurrency trading and cashback rewards, and internal tools for customer incident resolution.
  },
  {
    Enhanced system resilience and scalability by shifting from EC2 to a Kubernetes cluster, enabling effective horizontal scaling.
  },
  {
    Played a pivotal role in evolving from a monolithic REST framework to a more dynamic, distributed microservices architecture, utilizing NATS for enhanced performance and sophisticated data modeling.
  },
  {
    Collaborated in a multidisciplinary team, employing SCRUM methodology to rapidly and efficiently meet business objectives.
  }
}
%
\datedexperience{\href{https://mrhouston.net/en/}{mr Houston}}{August 2019 - November 2020}
\explanation{\textbfColor{Full Stack Developer}\emphColor{-\ \ \ Department of Artificial Intelligence.}}
\createbullets{
  {
    Developed a web interface for an AI application analyzing news impact on IBEX 35 share prices, employing Vue, Django, Flask and AWS Lambdas.
  },
  {
    Iteratively refined the application, identifying and implementing key use cases to attract potential clients.
  },
  {
    Resolved complex UI challenges and optimized query performance, enhancing application efficiency and user experience.
  },
  {
    Led the team in task allocation and priority setting, effectively meeting project deadlines.
  }
}
%
\datedexperience{\href{https://www.optivamedia.com/}{Optiva Media}}{June 2018 - October 2018}
\explanation{\textbfColor{Internship}\emphColor{-\ \ \ Web Developer}}
\createbullets{
  {
    Contributed to Media-Streamer, an ETL project for multimedia file metadata enrichment, utilizing AWS, MySQL, Sequelize, and ExpressJS.
  },
  {
    Gained initial experience in a SCRUM-based software development team, learning agile methodologies in practice.
  },
}

% Education
\section{Education} 
\datedexperience{\href{https://www.upm.es/}{Universidad Politécnica de Madrid}}{September 2018 - June 2019} 
\explanation{\textbfColor{Master in Cyber-Security}}
\createbullets{
  {
    \hspace{-0.25cm} \textbfColor{Graduate Project:} \hspace{-0.35cm} Researched, developed and deployed an email spam filter using a machine learning predictive model based on the Naive-Bayes algorithm.
  }
}
\datedexperience{\href{https://www.comillas.edu/icai}{Comillas ICAI}}{September 2013 - June 2018} 
\explanation{\textbfColor{Undergraduate Degree in Telematics Engineering}}
\createbullets{
  {
    \hspace{-0.3cm} \textbfColor{International Exchange Program:} \hspace{-0.35cm} Rose-Hulman Institute of Technology, Terre Haute, IN (4th year of undergrad)
  },
  {
    \hspace{-0.3cm} \textbfColor{Undergraduate Project:} \hspace{-0.28cm} Comprehensively researched the security risks present in automobile control systems and implemented an encrypted communication channel between the control components to alleviate the encountered issues. Sponsored by Rolls Royce, Indianapolis, IN.
  }
}

% Footnote
\createfootnote
\end{document}
